%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {CloneForce} % Organization
    {Remote} % Location
    {Nov. 2025 – Jun. 2026\newline Laid Off} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a platform for enterprises to provision and use LLM agents.}
        \item {Integrated with Twilio to enable communication with agents via SMS and WhatsApp.}
        \item {Built system to upload and normalize files for use in the knowledge base.}
        \item {Created tooling to migrate clones between the legacy and new systems.}
        \item {Used coding agents on a daily basis to accelerate development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Guideline} % Organization
    {Remote} % Location
    {Jun. 2025 – Aug. 2025\newline Laid Off} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added support for flexible billing to Guideline's 401k plans.}
        \item {Improved test coverage for document generation modules.}
        \item {Used Cursor and LLMs to assist with software engineering.}
        \item {Collaborated with other engineers and teams to solidify requirements for new features.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Iterative Health} % Organization
    {Remote} % Location
    {Feb. 2023 – Feb. 2025\newline Laid Off} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built web app for managing patient journeys using a React frontend and a Python FastAPI backend.}
        \item {Integrated with internal GraphQL service to manage patient journey data.}
        \item {Created a system for on-demand decomposition of video frames.}
        \item {Supported the machine learning team by creating new tools.}
        \item {Made improvements to ML pipeline as needed for new models and use cases.}
        \item {Helped standardize the ML model life cycle using containerization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Royal.io} % Organization
    {Remote} % Location
    {Aug. 2022 – Dec. 2022\newline Laid Off} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created generic meta transaction flow for handling various types of blockchain transactions.}
        \item {Worked on GraphQL interfaces for payments backend.}
        \item {Integrated with 3rd party vendors to on ramp and off ramp funds to and from the platform.}
        \item {Built gRPC endpoints to communicate between microservices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Decodable} % Organization
    {Remote} % Location
    {Jul. 2021 – Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented live streaming data preview on Apache Flink.}
        \item {Built system to deploy software across multi-tenant Kubernetes cluster.}
        \item {Created system to automatically access stream metadata in Decodable environment.}
        \item {Helped to build core streaming data platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Software Engineer} % Job title
    {Indeed.com} % Organization
    {Austin, TX} % Location
    {Aug. 2014 – Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led an internal incubator team working on a two-way marketplace for child care jobs.}
        \item {Worked on internal system for categorizing and routing sales leads.}
        \item {Implemented and supported internal tooling for other engineers.}
        \item {Created internal developer environment system using Bash and Python scripts around Docker.}
        \item {Maintained and improved internal deployment management webapp using a Soy template with jQuery frontend and a Java/Spring/Tomcat backend interfacing with Git, GitLab, and Atlassian APIs.}
        \item {Improved job posting JavaScript frontend using Closure library and compiler with Soy templates.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research \& Development Engineer} % Job title
    {IPsoft} % Organization
    {Austin, TX} % Location
    {Feb. 2013 – Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a geographically separated team in the creation of a new AI system for human interaction, supported by relational and graph databases.}
        \item {Managed the project using agile methodologies.}
        \item {Designed and implemented a first-order logic engine for interpreting and acting upon natural language.}
        \item {Conceived and realized the system for dynamically creating and executing new business processes.}
        \item {Fine-tuned module for understanding, analyzing, and storing natural language, then generating natural language responses.}
        \item {Demonstrated and explained the system to high-level executives at enterprise clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Google} % Organization
    {New York, NY} % Location
    {Feb. 2012 – Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed library for deploying video ads in client applications.}
        \item {Fixed bugs in Flash, JavaScript, iOS, and Android versions of the library.}
        \item {Designed and implemented an original new version of the Android library.}
        \item {Created a new version of the library for Samsung smart TV.}
        \item {Maintained and expanded unit and integration tests.}
        \item {Managed public releases of the library.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate Applications Engineer} % Job title
    {Micros Retail} % Organization
    {Solon, OH} % Location
    {Aug. 2010 – Mar. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Java point of sale application.}
        \item {Developed and deployed iOS point of sale application.}
        \item {Designed and implemented customer-specific modifications.}
        \item {Worked with quality assurance and customers to determine requirements and resolve issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
